```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Top dogs

In this homework, you will try to reproduce the fantastic infographic for [top dogs](https://informationisbeautiful.net/visualizations/best-in-show-whats-the-top-data-dog/), originally produced by David McCandless. The raw data can be found [here](https://docs.google.com/spreadsheets/d/1l_HfF5EaN-QgnLc2UYdCc7L2CVrk0p3VdGB1godOyhk/edit#gid=10). You can download this file by File -- Download As -- Microsoft Excel (.xlsx).

**Submission instructions**: Create a folder named `ds202_hw6`, and name the RMarkDown file including your solutions `hw6.Rmd` under this folder. For the submission, create a GitHub repository named `ds202_hw6` under your GitHub account, and push both `hw6.Rmd` and the knitted `hw6.html` before the deadline. I will assume you use the same GitHub username as for your HW5 submission. The latest version of your homework appearing on GitHub before the deadline is graded. *It is crucial to follow the exact folder structure and file names*, so that your homework can be reproduced and graded by an automated script. This homework is **due on April 22** before class.

1. Import the data and clean appropriately. To read in the data, you can use `readxl::read_xlsx('fileNameHere', sheet='sheetNameHere')`. Required data are in the sheets `Best in show` and `Best in show full sheet`. Take extra care on the column names and the first few rows of the data frame after read in.

```{r}
library(tidyverse)
library(ggplot2)
library(dplyr)

bestInShow <- readxl::read_xlsx('bestInShow.xlsx', sheet='Best in show')
fullSheet <- readxl::read_xlsx('bestInShow.xlsx', sheet='Best in show full sheet')

#All info can be found in the full sheet
#Select columns by number
fullSheet <- fullSheet %>% select(1, 3, 32, 5, 6, 11) %>% slice(4:177) %>% drop_na()

#Rename:
newNames <- c('Breed', 'Type', 'Size', 'Data Score', 'Popularity', 
                    'Intelligence')

colnames(fullSheet) <- newNames

str(fullSheet)
fullSheet$`Data Score` <- as.numeric(fullSheet$`Data Score`)
fullSheet$`Popularity` <- as.numeric(fullSheet$`Popularity`)
fullSheet$`Intelligence` <- as.numeric(fullSheet$`Intelligence`)
fullSheet$Size <- as.factor(fullSheet$Size)
```

2. Create a graphics similar to the  [top dogs](https://informationisbeautiful.net/visualizations/best-in-show-whats-the-top-data-dog/) figure. Your figure needs to display the following information with appropriate plotting elements:

- breed of dog x
- type of dog (work, toy, etc.) x
- size of dog 
- data score x
- popularity x
- intelligence of the dog 
- appropriate legends & explanation

Hints and Notes:

- The breed of dog can be displayed without the silhouttes (text only is fine)
- Avoid (too much) overlaps!
- Choose a good color scheme.
- Your submission is supposed to be fully reproducible, i.e. the TA and I will 'knit' your submission in RStudio. 

```{r}
fullSheet %>% ggplot(aes(x=`Data Score`, y=Popularity, 
                         color=Intelligence, size=Type, shape=Size)) + 
  geom_text(label=fullSheet$Breed, check_overlap = TRUE) +
  geom_point(alpha = .5) + 
  xlim(.7, 4.2) + scale_color_continuous(low='black', high='red') + 
  theme(legend.position = 'bottom', legend.title = element_text( size=5), 
        legend.text = element_text(size=5)) + ggtitle("Best in Show: The Ultimate Dog Data")
```







